Illuminating a Dark Lens : A Type Ia Supernova Magnified by \\ the \changeR{Frontier Fields} Galaxy Cluster Abell 2744

### 2015-05-22 snTomas.tex
final comments and author additions before submission

\noindent The inferred magnifications for the two different fitters are
reported in the final column of Table~\ref{tab:MeasuredMagnification}.

>>>>

\noindent The inferred magnifications for the two different fitters are
reported in the final column of Table~\ref{tab:MeasuredMagnification}.
\changeR{
Although we have chosen to use a cosmology-independent approach to
determine the magnifications, we note that these results are fully
consistent with the values that would be determined by comparing the
observed SN \tomas\ distance modulus against the predicted value from
a flat \LCDM\ cosmology. Adopting the cosmological parameters used
in \citetalias{Patel:2014} and derived in \citet{Sullivan:2011}
(\Ho=71.6, \Om=0.27, \OL=0.73) would give a predicted distance modulus
$dm_{\Lambda CDM}=44.90$ and a measured magnification $\mu=1.9$.
Substituting alternative cosmological
parameters \citep[e.g.,][]{Betoule:2014,Planck:2015} would not
significantly change the inferred magnification or affect our
conclusions.
}
